### 2020-04-12 Thesis-Chapter1-Introduction.tex
Work on intro, background
Simplify premises/principles

\Acl{EA} is a wicked problem. In encryption policy, \ac{EA} is alternative means of decryption reserved for law
enforcement use. Characterized by a dynamic technological environment, disagreement about underlying values, and
resistance to a clear solution, the debate on \acl{EA} refuses to end. This paper will not attempt to end the debate,
but to inform it with additional structure.

@@

Most importantly, in the pursuit of data privacy, regulatory action is part of the threat model. If the technical
community fails to act but regulators move forward, everyone may become subject to technically misguided laws that do
great harm. Bad \ac{EA} policy is just as much a threat as poor passwords.

@@

This paper accepts and builds on the following premises, some of which were introduced in \mysec{sec-motivation}. These
premises are not principles for potential \ac{EA} designs, but the starting place for discussing the \ac{EA} debate.

@@

\principle{The discussion must go on} As long as regulators continue pursuing \ac{EA} regulation, it is the
responsibility of the technical community to engage and respect the valid arguments being presented.

\principle{Cryptography is foundational} Strong cryptography in its various forms is foundational to digital security.

\principle{Investigators need data} The ability to access digital data for investigation and prosecution is important
today and will be increasingly important in the future.

\principle{Mass surveillance is a danger} Mass surveillance, which \ac{EA} makes easier, is a grave danger from which
representative governments are not immune.

\principle{Transparency is necessary} Transparency of the law enforcement and intelligence communities' data access
capability and usage is critical for public trust.

\principle{\Ac{EA} is an international problem} The internet is largely borderless, and international and human rights
considerations significantly constrain workable \ac{EA} solutions.

\principle{Perfection is not the goal} To loosely quote the ``insecurity axioms,'' insecurity cannot be destroyed, only
moved around \cite{nrc_schneider_1999}. \Ac{EA}, like all security, is a matter of finding the right balance of risk.

@@

The paper serves to clarify the arguments composing debate and the nature of the technical problem. After reproducing a
brief U.S.-focused history of encryption regulation, technology, and conflict, it introduces argument maps and threat
models using data flow diagrams. In the following chapters it analyzes exceptional access arguments in detail and
creates a multi-level threat model, broken down by the significantly different challenges posed by \ac{DAR} and
\ac{DIM}. The paper concludes with a set of policies and principles to apply to the problem in light of valid arguments
and threats.

>>>>

\Acl{EA} is a wicked problem. In encryption policy, \ac{EA} is alternative means of decryption intended for law
enforcement use. Characterized by a dynamic technological environment, disagreement about underlying values, and
resistance to a clear solution, the debate on \acl{EA} refuses to end. This paper will not attempt to end the debate,
but to inform it with additional structure.

@@

Most importantly, in the pursuit of data privacy, regulatory action is part of the threat model. If the technical
community fails to act but regulators move forward, everyone may become subject to technically misguided laws that do
great harm. Bad \ac{EA} policy is just as much a threat as poor passwords. Due to this threat, as long as lawmakers
continue pursuing \ac{EA} regulation, it is the responsibility of the technical community to engage in discussion and
respond to the arguments being presented.

@@

This paper accepts and builds on the following premises. These premises are not principles for potential \ac{EA}
designs, but the starting place for discussing the \ac{EA} debate.

@@

\principle{Cybersecurity is critical} With current levels of reliance on computer information systems, cybersecurity is
critical to the wellbeing of society. Two important elements of cybersecurity are cryptography and system architecture.
Policy which supports security does not undercut cryptographic integrity or require high-risk architectures.

\principle{Absolute privacy is not an absolute right} Certain rights supersede the legitimate claims of government, but
absolute privacy is not one of them. In some contexts, absolute privacy is proper, and in almost all contexts,
reasonable privacy should be presumed. However, privacy is not an absolute right, and investigators should have access
to some classes of data. Access to these classes of data is important today and will be increasingly important in the
future.

\principle{\Ac{EA} is an inherently complex problem} The factors factors that make \ac{EA} a \ac{wicked-prob} mean that
proposed solutions must be analyzed at many levels. Some these factors are \ac{EA}'s relation to mass surveillance,
potential for abuse, international reception, economic impact, and need for transparency.

\principle{Perfection is not the standard} Wicked policy problems do not have perfect solutions, or even verifiably
optimal solutions, so we cannot use perfection as the standard. To quote the ``insecurity axioms,'' insecurity cannot be
destroyed, only moved around \cite{nrc_schneider_1999}. \Ac{EA}, like all security problems, is a matter of finding the
right balance of risk given the threats under consideration--which includes regulatory action.

@@

The paper serves to clarify the arguments composing debate and the nature of the technical problem. After reproducing a
brief U.S.-focused history of encryption regulation, technology, and conflict, it introduces argument maps and threat
models using data flow diagrams. In the following chapters it analyzes exceptional access arguments in detail and
creates a multi-level threat model, broken down by the significantly different challenges posed by \acl{DAR} and
\acl{DIM}. The paper concludes with a set of policies and principles to apply to the problem in light of valid arguments
and threats.
